---
title: "Final_Project_Analysis"
author: "Yoolim Jin, 22612692"
date: "2015년 12월 9일"
output: 
  pdf_document: 
    latex_engine: xelatex
---
Complete function for taking the weighted average of relative frequency per year
```{r, echo = FALSE}
rel_freq <- function(file, data = "data") { #x is the clean data_frame file
  x <- read.csv(file)
  y <- NULL
  for (i in 2006:2013) {
    a <- which(x$from_year == i & x$to_year == i)
    b <- NULL
    for (j in 1:length(a)) {
      b[j] <- x[a[j], data]
    } 
    sum1 <- sum(b*7)
    c <- setdiff(which(x$from_year == i | x$to_year == i), a)
    d <- NULL
    for (k in 1:length(c)) {
      if(x[c[k], 'from_year'] == i) {
        d[k] <- (31 - x[c[k], 'from_day'] + 1) * x[c[k], data]
      } else if(x[c[k], 'to_year'] == i) {
        d[k] <- x[c[k], 'from_day'] * x[c[k], data]
      }
    } 
    sum2 <- sum(d)
    e <- as.numeric(as.Date(paste(i, 12, 31, sep = '-')) - 
                      as.Date(paste(i, 1, 1, sep = '-')) + 1)
    y[i - 2005] <- (sum1 + sum2)/e
  } 
  names(y) <- 2006:2013
  return(y)
}
```
Finding averages of each year based on clean data
```{r, echo = FALSE}
#inflation
rel_freq('./data/google/inflation/clean_inf_Canada.csv')
rel_freq('./data/google/inflation/clean_inf_South_Africa.csv')
rel_freq('./data/google/inflation/clean_inf_NZ.csv')
rel_freq('./data/google/inflationclean_inf_US.csv')
#unemployment
rel_freq('./data/google/unemployment/clean_unemp_Canada.csv')
rel_freq('./data/google/unemployment/clean_unemp_South_Africa.csv')
rel_freq('./data/google/unemployment/clean_unemp_NZ.csv')
rel_freq('./data/google/unemployment/clean_unemp_US.csv')
```
Store the base data
```{r, echo = FALSE}
#World Inflation
world_inflation <- read.csv("./data/Worldbank/Inflation/clean_World_Inflation.csv", 
                            check.names = FALSE, row.names = 1)
#World Unemployment
world_unemployment <- read.csv("./data/Worldbank/unemployment/clean_world_unemployment.csv", 
                               check.names = FALSE, row.names = 1)
#Google Inflation
GCan_inf <- rel_freq('./data/google/inflation/clean_inf_Canada.csv')
GSA_inf <- rel_freq('./data/google/inflation/clean_inf_South_Africa.csv')
GNZ_inf <- rel_freq('./data/google/inflation/clean_inf_NZ.csv')
GUS_inf <- rel_freq('./data/google/inflation/clean_inf_US.csv')
#Google Unemployment
GCan_unemp <- rel_freq('./data/google/unemployment/clean_unemp_Canada.csv')
GSA_unemp <- rel_freq('./data/google/unemployment/clean_unemp_South_Africa.csv')
GNZ_unemp <- rel_freq('./data/google/unemployment/clean_unemp_NZ.csv')
GUS_unemp<- rel_freq('./data/google/unemployment/clean_unemp_US.csv')
```
1) See the relationship between Unemployment and Inflation between different countries using World Bank data
```{r, echo = FALSE}
par(mfrow=c(2,2),oma = c(1, 0, 1, 0))
par(mar = c(3.5, 4, 4, 2) + 0.1)
#Canada
plot(world_unemployment$Canada, world_inflation$Canada, main = "Canada",
     xlab = "", ylab = "", pch = 15, las = 1)
mtext("Unemployment %", side=1, col=rgb(0, 0, 0),line=2.25, cex = 0.7)
mtext("Inflation %", side=2, col=rgb(0, 0, 0),line=2.75, cex = 0.7)
abline(lm(world_inflation$Canada~world_unemployment$Canada), 
       col = rgb(1, 0, 0), lwd = 4)
cor(world_unemployment$Canada, world_inflation$Canada)
#New Zealand
plot(world_unemployment$`New Zealand`, world_inflation$`New Zealand`, 
     main = "New Zealand", 
     xlab = "", ylab = "", pch = 15, las = 1)
mtext("Unemployment %", side=1, col=rgb(0, 0, 0),line=2.25, cex = 0.7)
mtext("Inflation %", side=2, col=rgb(0, 0, 0),line=2.75, cex = 0.7)
abline(lm(world_inflation$`New Zealand`~world_unemployment$`New Zealand`), 
       col = rgb(1, 0, 0), lwd = 4)
cor(world_unemployment$`New Zealand`, world_inflation$`New Zealand`)
#South Africa
plot(world_unemployment$`South Africa`, world_inflation$`South Africa`, 
     main = "South Africa", 
     xlab = "", ylab = "", pch = 15, las = 1)
mtext("Unemployment %", side=1, col=rgb(0, 0, 0),line=2.25, cex = 0.7)
mtext("Inflation %", side=2, col=rgb(0, 0, 0),line=2.5, cex = 0.7)
abline(lm(world_inflation$`South Africa`~world_unemployment$`South Africa`), 
       col = rgb(1, 0, 0), lwd = 4)
mtext("Unemployment-Inflation Comparison(World Data)", outer = TRUE, 
      cex = 1, line = -1, font = 2)
cor(world_unemployment$`South Africa`, world_inflation$`South Africa`)
#United States
plot(world_unemployment$`United States`, world_inflation$`United States`, 
     main = "United States", 
     xlab = "", ylab = "", pch = 15, las = 1)
mtext("Unemployment %", side=1, col=rgb(0, 0, 0),line=2.25, cex = 0.7)
mtext("Inflation %", side=2, col=rgb(0, 0, 0),line=2.55, cex = 0.7)
abline(lm(world_inflation$`United States`~world_unemployment$`United States`), 
       col = rgb(1, 0, 0), lwd = 4)
cor(world_unemployment$`United States`, world_inflation$`United States`)
```


  2a)Graphical Comparisons(Unemployment)
```{r, echo = FALSE}
par(mfrow=c(2,2),oma = c(1, 0, 1, 0))
#Canada
par(mar=c(3.5, 4, 4, 5) + 0.1)
plot(world_unemployment$`Canada`, xlab = "", ylab = "", main = "Canada",
     axes = FALSE, type = "b", pch = 16)
axis(2, at = seq(6, 8, by = 0.5), col=rgb(0, 0, 0),las=1)
mtext("Unemployment %",side=2,line=2.5, cex = 0.7)
box()
par(new = TRUE)
plot(GCan_unemp, pch = 15, type = 'b', xlab = '', ylab = '', main = '', 
     axes = FALSE, col = rgb(1, 0, 0))
axis(4, at = seq(10, 60, by = 10), col = rgb(1, 0, 0), 
     col.axis = rgb(1, 0, 0), las = 1)
mtext("Google", side=4,col=rgb(1, 0, 0),line=2.5, cex = 0.7) 
axis(1, at = 1:8, labels = seq(2006, 2013, by = 1), las = 1)
mtext("Years", side=1, col=rgb(0, 0, 0),line=2.5, cex = 0.7) 
#New Zealand
par(mar=c(3.5, 4, 4, 5) + 0.1)
plot(world_unemployment$`New Zealand`, xlab = "", ylab = "", main = "New Zealand",
     axes = FALSE, type = "b", pch = 16)
axis(2, at = seq(4, 7, by = 0.5), col=rgb(0, 0, 0),las=1)
mtext("Unemployment %",side=2,line=2.5, cex = 0.7)
box()
par(new = TRUE)
plot(GCan_unemp, pch = 15, type = 'b', xlab = '', ylab = '', 
     main = '', axes = FALSE, col = rgb(1, 0, 0))
axis(4, at = seq(15, 60, by = 10), col = rgb(1, 0, 0), 
     col.axis = rgb(1, 0, 0), las = 1)
mtext("Google", side=4,col=rgb(1, 0, 0),line=2.5, cex = 0.7) 
axis(1, at = 1:8, labels = seq(2006, 2013, by = 1), las = 1)
mtext("Years", side=1, col=rgb(0, 0, 0),line=2.5, cex = 0.7) 
mtext("Unemployment-Google Comparison", outer = TRUE, cex = 1, line = -1, font = 2)
#South Africa
par(mar=c(3.5, 4, 4, 5) + 0.1)
plot(world_unemployment$`South Africa`, xlab = "", ylab = "", main = "South Africa",
     axes = FALSE, type = "b", pch = 16)
axis(2, at = seq(22.5, 25.5, by = 0.5), col=rgb(0, 0, 0),las=1)
mtext("Unemployment %",side=2, line=3, cex = 0.7)
box()
par(new = TRUE)
plot(GSA_unemp, pch = 15, type = 'b', xlab = '', ylab = '', main = '', 
     axes = FALSE, col = rgb(1, 0, 0))
axis(4, at = seq(10, 40, by = 5), col = rgb(1, 0, 0), col.axis = rgb(1, 0, 0), las = 1)
mtext("Google", side=4, col=rgb(1, 0, 0),line=2.5, cex = 0.7) 
axis(1, at = 1:8, labels = seq(2006, 2013, by = 1), las = 1)
mtext("Years", side=1, col=rgb(0, 0, 0),line=2.5, cex = 0.7) 
#United States
par(mar=c(3.5, 4, 4, 5) + 0.1)
plot(world_unemployment$`United States`, xlab = "", ylab = "", main = "US",
     axes = FALSE, type = "b", pch = 16)
axis(2, at = seq(4, 10, by = 1), col = rgb(0, 0, 0),las=1)
mtext("Unemployment %",side=2,line=2.5, cex = 0.7)
box()
par(new = TRUE)
plot(GUS_unemp, pch = 15, type = 'b', xlab = '', ylab = '', main = '', 
     axes = FALSE, col = rgb(1, 0, 0))
axis(4, at = seq(0, 70, by = 10), col = rgb(1, 0, 0), 
     col.axis = rgb(1, 0, 0), las = 1)
mtext("Google", side=4, col=rgb(1, 0, 0), line=2.5, cex = 0.7) 
axis(1, at = 1:8, labels = seq(2006, 2013, by = 1), las = 1)
mtext("Years", side=1, col=rgb(0, 0, 0),line=2.5, cex = 0.7)
par(mfrow = c(1, 1))
legend("center", c("World Bank Data", "Google Trends Data"), lty=1, lwd=5, 
       col=c(rgb(0, 0, 0), rgb(1, 0, 0)), cex = 0.8, horiz = TRUE)
```


  2b)Graphical Comparison(Inflation)
```{r, echo = FALSE}
par(mfrow=c(2,2),oma = c(1, 0, 1, 0))
#Canada
par(mar=c(3.5, 4, 4, 5) + 0.1)
plot(world_inflation$`Canada`, xlab = "", ylab = "", main = "Canada",
     axes = FALSE, type = "b", pch = 16)
axis(2, at = seq(0.5, 3, by = 0.5), col=rgb(0, 0, 0),las=1)
mtext("Inflation %",side=2,line=2.5, cex = 0.7)
box()
par(new = TRUE)
plot(GCan_inf, pch = 15, type = 'b', xlab = '', ylab = '', 
     main = '', axes = FALSE, col = rgb(1, 0, 0))
axis(4, at = seq(30, 46, by = 2), col = rgb(1, 0, 0), 
     col.axis = rgb(1, 0, 0), las = 1)
mtext("Google Freq", side=4, col=rgb(1, 0, 0),line=2.5, cex = 0.7) 
axis(1, at = 1:8, labels = seq(2006, 2013, by = 1), las = 1)
mtext("Years", side=1, col=rgb(0, 0, 0),line=2.5, cex = 0.7)
#New Zealand
par(mar=c(3.5, 4, 4, 5) + 0.1)
plot(world_inflation$`New Zealand`, xlab = "", ylab = "", main = "New Zealand",
     axes = FALSE, type = "b", pch = 16)
axis(2, at = seq(0, 4.5, by = 0.5), col=rgb(0, 0, 0),las=1)
mtext("Inflation %",side=2,line=2.5, cex = 0.7)
box()
par(new = TRUE)
plot(GNZ_inf, pch = 15, type = 'b', xlab = '', ylab = '', main = '', 
     axes = FALSE, col = rgb(1, 0, 0))
axis(4, at = seq(2, 20, by = 2), col = rgb(1, 0, 0), col.axis = rgb(1, 0, 0), las = 1)
mtext("Google Freq", side=4,col=rgb(1, 0, 0),line=2.5, cex = 0.7) 
axis(1, at = 1:8, labels = seq(2006, 2013, by = 1), las = 1)
mtext("Years", side=1, col=rgb(0, 0, 0),line=2.5, cex = 0.7)
mtext("Inflation-Google Comparison", outer = TRUE, cex = 1, line = -1, font = 2)
#South Africa
par(mar=c(3.5, 4, 4, 5) + 0.1)
plot(world_inflation$`South Africa`, xlab = "", ylab = "", main = "South Africa",
     axes = FALSE, type = "b", pch = 16)
axis(2, at = seq(4, 12, by = 2), col=rgb(0, 0, 0),las=1)
mtext("Inflation %",side=2,line=2.5, cex = 0.7)
box()
par(new = TRUE)
plot(GSA_inf, pch = 15, type = 'b', xlab = '', ylab = '', main = '', 
     axes = FALSE, col = rgb(1, 0, 0))
axis(4, at = seq(0, 35, by = 5), col = rgb(1, 0, 0), col.axis = rgb(1, 0, 0), las = 1)
mtext("Google Freq", side=4,col=rgb(1, 0, 0),line=2.5, cex = 0.7) 
axis(1, at = 1:8, labels = seq(2006, 2013, by = 1), las = 1)
mtext("Years", side=1, col=rgb(0, 0, 0),line=2.5, cex = 0.7) 
#United States
par(mar=c(3.5, 4, 4, 5) + 0.1)
plot(world_inflation$`United States`, xlab = "", ylab = "", main = "US",
     axes = FALSE, type = "b", pch = 16)
axis(2, at = seq(0, 4, by = 1), col=rgb(0, 0, 0),las=1)
mtext("Inflation %",side=2,line=2.5, cex = 0.7)
box()
par(new = TRUE)
plot(GUS_inf, pch = 15, type = 'b', xlab = '', ylab = '', main = '', 
     axes = FALSE, col = rgb(1, 0, 0))
axis(4, at = seq(30, 60, by = 5), col = rgb(1, 0, 0), col.axis = rgb(1, 0, 0), las = 1)
mtext("Google Trend", side = 4, col = rgb(1, 0, 0), line=2.5, cex = 0.7) 
axis(1, at = 1:8, labels = seq(2006, 2013, by = 1), las = 1)
mtext("Years", side=1, col=rgb(0, 0, 0),line=2.5, cex = 0.7) 
par(mfrow = c(1, 1))
legend("center", c("World Bank Data", "Google Trends Data"), lty=1, lwd=5, 
       col=c(rgb(0, 0, 0), rgb(1, 0, 0)), cex = 0.8, horiz = TRUE)
```


3) See the relationship between Unemployment and Inflation between different countries using Google data
```{r, echo = FALSE}
par(mfrow=c(2,2),oma = c(1, 0, 1, 0))
#Canada
par(mar = c(3.5, 4, 4, 2) + 0.1)
plot(GCan_unemp, GCan_inf, 
     main = "Canada", 
     xlab = "", ylab = "", pch = 16, las = 1)
mtext("Unemployment Search Freq", side=1, col=rgb(0, 0, 0),line=2.25, cex = 0.7)
mtext("Inflation Search Freq", side=2, col=rgb(0, 0, 0),line=2.75, cex = 0.7)
abline(lm(GCan_inf~GCan_unemp), col = rgb(1, 0, 0), lwd = 4)
cor(GCan_inf, GCan_unemp)
#New Zealand
par(mar = c(3.5, 4, 4, 2) + 0.1)
plot(GNZ_unemp, GNZ_inf, 
     main = "New Zealand", 
     xlab = "", ylab = "", pch = 16, las = 1)
mtext("Unemployment Search Freq", side=1, col=rgb(0, 0, 0),line=2.25, cex = 0.7)
mtext("Inflation Search Freq", side=2, col=rgb(0, 0, 0),line=2.75, cex = 0.7)
abline(lm(GNZ_inf~GNZ_unemp), col = rgb(1, 0, 0), lwd = 4)
cor(GNZ_inf, GNZ_unemp)
mtext("Inflation-Unemployment Comparison(Google)", outer = TRUE, 
      cex = 1, line = -1, font = 2)
#South Africa
par(mar = c(3.5, 4, 4, 2) + 0.1)
plot(GSA_unemp, GSA_inf, 
     main = "South Africa", 
     xlab = "", ylab = "", pch = 16, las = 1)
mtext("Unemployment Search Freq", side=1, col=rgb(0, 0, 0),line=2.25, cex = 0.7)
mtext("Inflation Search Freq", side=2, col=rgb(0, 0, 0),line=2.75, cex = 0.7)
abline(lm(GSA_inf~GSA_unemp), col = rgb(1, 0, 0), lwd = 4)
cor(GSA_inf, GSA_unemp)
#United States
par(mar = c(3.5, 4, 4, 2) + 0.1)
plot(GUS_unemp, GUS_inf, 
     main = "United States", 
     xlab = "", ylab = "", pch = 16, las = 1)
mtext("Unemployment Search Freq", side=1, col=rgb(0, 0, 0),line=2.25, cex = 0.7)
mtext("Inflation Search Freq", side=2, col=rgb(0, 0, 0),line=2.75, cex = 0.7)
abline(lm(GUS_inf~GUS_unemp), col = rgb(1, 0, 0), lwd = 4)
cor(GUS_inf, GUS_unemp)
```


4)Graphical Comparison of Phillips Curve (World Data vs. Google)
```{r, echo = FALSE}
par(mfrow=c(2,2),oma = c(1, 0, 1, 0))
#Canada
par(mar=c(3.5, 4, 5.25, 5) + 0.1)
plot(world_unemployment$`Canada`, world_inflation$`Canada`, 
     main = "", 
     xlab = "", ylab = "", pch = 15, axes = FALSE)
abline(lm(world_inflation$`Canada`~world_unemployment$`Canada`), 
       col = rgb(0, 0, 0), lwd = 4)
axis(2, at = seq(0.5, 3, by = 0.5), col=rgb(0, 0, 0),las=1)
mtext("Inflation %", side=2, col=rgb(0, 0, 0),line=2.5, cex = 0.7) 
axis(1, at = seq(6, 8, by = 0.5), col=rgb(0, 0, 0),las=1)
mtext("Unemployment %", side=1, col=rgb(0, 0, 0),line=2, cex = 0.7) 
box()
par(new = TRUE)
plot(GCan_unemp, GCan_inf,
     xlab = "", ylab = "", pch = 16, axes = FALSE, col = rgb(1, 0, 0), main = '')
axis(4, at = seq(30, 44, by = 2), col=rgb(1, 0, 0),las=1, col.axis = rgb(1, 0, 0))
mtext("Inflation Search Freq", side=4, col=rgb(1, 0, 0),line=2, cex = 0.7) 
axis(3, at = seq(10, 60, by = 5), col=rgb(1, 0, 0),las=1, col.axis = rgb(1, 0, 0))
mtext("Unemployment Search Freq", side=3, col=rgb(1, 0, 0),line=2, cex = 0.7) 
abline(lm(GCan_inf~GCan_unemp), col = rgb(1, 0, 0), lwd = 4)
title("Canada", line = 3.5)
#New Zealand
par(mar=c(3.5, 4, 5.25, 5) + 0.1)
plot(world_unemployment$`New Zealand`, world_inflation$`New Zealand`, 
     main = "", 
     xlab = "", ylab = "", pch = 15, axes = FALSE)
abline(lm(world_inflation$`New Zealand`~world_unemployment$`New Zealand`), 
       col = rgb(0, 0, 0), lwd = 4)
axis(2, at = seq(0, 4, by = 1), col=rgb(0, 0, 0),las=1)
mtext("Inflation %", side=2, col=rgb(0, 0, 0),line=2, cex = 0.7) 
axis(1, at = seq(4, 7, by = 0.5), col=rgb(0, 0, 0),las=1)
mtext("Unemployment %", side=1, col=rgb(0, 0, 0),line=2, cex = 0.7) 
box()
par(new = TRUE)
plot(GNZ_unemp, GNZ_inf,
     xlab = "", ylab = "", pch = 16, axes = FALSE, col = rgb(1, 0, 0), main = '')
axis(4, at = seq(0, 20, by = 2.5), col=rgb(1, 0, 0),las=1, col.axis = rgb(1, 0, 0))
mtext("Inflation Search Freq", side=4, col=rgb(1, 0, 0),line=2.5, cex = 0.7) 
axis(3, at = seq(0, 50, by = 5), col=rgb(1, 0, 0),las=1, col.axis = rgb(1, 0, 0))
mtext("Unemployment Search Freq", side=3, col=rgb(1, 0, 0),line=2, cex = 0.7) 
abline(lm(GNZ_inf~GNZ_unemp), col = rgb(1, 0, 0), lwd = 4)
title("New Zealand", line = 3.5)
#South Africa
par(mar=c(3.5, 4, 5.25, 5) + 0.1)
plot(world_unemployment$`South Africa`, world_inflation$`South Africa`, 
     main = "", 
     xlab = "", ylab = "", pch = 15, axes = FALSE)
abline(lm(world_inflation$`South Africa`~world_unemployment$`South Africa`), 
       col = rgb(0, 0, 0), lwd = 4)
axis(2, at = seq(4, 12, by = 2), col=rgb(0, 0, 0),las=1)
mtext("Inflation %", side=2, col=rgb(0, 0, 0),line=2, cex = 0.7) 
axis(1, at = seq(22, 25, by = 0.5), col=rgb(0, 0, 0),las=1)
mtext("Unemployment %", side=1, col=rgb(0, 0, 0),line=2, cex = 0.7) 
box()
par(new = TRUE)
plot(GSA_unemp, GSA_inf,
     xlab = "", ylab = "", pch = 16, axes = FALSE, col = rgb(1, 0, 0), main = '')
axis(4, at = seq(5, 40, by = 5), col=rgb(1, 0, 0),las=1, col.axis = rgb(1, 0, 0))
mtext("Inflation Search Freq", side=4, col=rgb(1, 0, 0),line=2, cex = 0.7) 
axis(3, at = seq(10, 40, by = 5), col=rgb(1, 0, 0),las=1, col.axis = rgb(1, 0, 0))
mtext("Unemployment Search Freq", side=3, col=rgb(1, 0, 0),line=2, cex = 0.7) 
abline(lm(GSA_inf~GSA_unemp), col = rgb(1, 0, 0), lwd = 4)
title("South Africa", line = 3.5)
#United States
par(mar=c(3.5, 4, 5.25, 5) + 0.1)
plot(world_unemployment$`United States`, world_inflation$`United States`, 
     main = "", 
     xlab = "", ylab = "", pch = 15, axes = FALSE)
abline(lm(world_inflation$`United States`~world_unemployment$`United States`), 
       col = rgb(0, 0, 0), lwd = 4)
axis(2, at = seq(0, 4, by = 1), col=rgb(0, 0, 0),las=1)
mtext("Inflation %", side=2, col=rgb(0, 0, 0),line=2, cex = 0.7) 
axis(1, at = seq(5, 9, by = 1), col=rgb(0, 0, 0),las=1)
mtext("Unemployment %", side=1, col=rgb(0, 0, 0),line=2, cex = 0.7) 
box()
par(new = TRUE)
plot(GUS_unemp, GUS_inf,
     xlab = "", ylab = "", pch = 16, axes = FALSE, col = rgb(1, 0, 0), main = '')
axis(4, at = seq(30, 60, by = 5), col=rgb(1, 0, 0),las=1, col.axis = rgb(1, 0, 0))
mtext("Inflation Search Freq", side=4, col=rgb(1, 0, 0),line=2, cex = 0.7) 
axis(3, at = seq(10, 70, by = 10), col=rgb(1, 0, 0),las=1, col.axis = rgb(1, 0, 0))
mtext("Unemployment Search Freq", side=3, col=rgb(1, 0, 0),line=2, cex = 0.7) 
abline(lm(GUS_inf~GUS_unemp), col = rgb(1, 0, 0), lwd = 4)
title("US", line = 3.5)
mtext("Phillips Curve(Actual vs. Google)", outer = TRUE, cex = 1, line = -1, font = 2)
par(mfrow = c(1, 1))
legend('bottom', c("World Bank Data", "Google Trends Data"), lty=1, lwd=5, 
       col=c(rgb(0, 0, 0), rgb(1, 0, 0)), cex = 0.8, horiz = TRUE, inset = 0.6)
```
