---
title: "Final_Project_Analysis"
author: "Yoolim Jin, 22612692"
date: "2015년 12월 9일"
output: pdf_document
---
Complete function for taking the weighted average of relative frequency per year
```{r}
rel_freq <- function(file, data = "inflation") { #x is the clean data_frame file
  x <- read.csv(file)
  y <- NULL
  for (i in 2006:2013) {
    a <- which(x$from_year == i & x$to_year == i)
    b <- NULL
    for (j in 1:length(a)) {
      b[j] <- x[a[j], data]
    } 
    sum1 <- sum(b*7)
    c <- setdiff(which(x$from_year == i | x$to_year == i), a)
    d <- NULL
    for (k in 1:length(c)) {
      if(x[c[k], 'from_year'] == i) {
        d[k] <- (31 - x[c[k], 'from_day'] + 1) * x[c[k], data]
      } else if(x[c[k], 'to_year'] == i) {
        d[k] <- x[c[k], 'from_day'] * x[c[k], data]
      }
    } 
    sum2 <- sum(d)
    e <- as.numeric(as.Date(paste(i, 12, 31, sep = '-')) - as.Date(paste(i, 1, 1, sep = '-')) + 1)
    y[i - 2005] <- (sum1 + sum2)/e
  } 
  names(y) <- 2006:2013
  return(y)
}
```
Store the base data
```{r}
#World Inflation
setwd("/Users/Ispyarion/Desktop/Project/data/Worldbank/Inflation")
world_inflation <- read.csv("clean_World_Inflation.csv", check.names = FALSE, row.names = 1)
#World Unemployment
setwd("/Users/Ispyarion/Desktop/Project/data/Worldbank/Unemployment")
world_unemployment <- read.csv("clean_world_unemployment.csv", check.names = FALSE, row.names = 1)
#Google Inflation
setwd("/Users/Ispyarion/Desktop/Project/data/google/inflation")
GNig_inf <- rel_freq('clean_inf_Nigeria.csv', data = 'inflation')
GCan_inf <- rel_freq('clean_inf_Canada.csv', data = 'inflation')
GSA_inf <- rel_freq('clean_inf_South_Africa.csv', data = 'inflation')
GNZ_inf <- rel_freq('clean_inf_NZ.csv', data = 'inflation')
GUS_inf <- rel_freq('clean_inf_US.csv', data = 'inflation')
#Google Unemployment
setwd("/Users/Ispyarion/Desktop/Project/data/google/unemployment")
GNig_unemp <- rel_freq('clean_unemp_Nigeria.csv', data = 'unemployment')
GCan_unemp <- rel_freq('clean_unemp_Canada.csv', data = 'unemployment')
GSA_unemp <- rel_freq('clean_unemp_South_Africa.csv', data = 'unemployment')
GNZ_unemp <- rel_freq('clean_unemp_NZ.csv', data = 'unemployment')
GUS_unemp<- rel_freq('clean_unemp_US.csv', data = 'unemployment')
```
1) See the relationship between Unemployment and Inflation between different countries using World Bank data
```{r}
par(mar = c(5, 4, 4, 2) + 0.1)
#Canada
plot(world_unemployment$Canada, world_inflation$Canada, main = "Unemployment vs. Inflation (Canada)", 
     xlab = "Canada Unemployment Rate", ylab = "Canada Inflation Rate", pch = 15)
abline(lm(world_inflation$Canada~world_unemployment$Canada), col = 'red', lwd = 4)
cor(world_unemployment$Canada, world_inflation$Canada)
#New Zealand
plot(world_unemployment$`New Zealand`, world_inflation$`New Zealand`, 
     main = "Unemployment vs. Inflation (New Zealand)", 
     xlab = "New Zealand Unemployment Rate", ylab = "New Zealand Inflation Rate", pch = 15)
abline(lm(world_inflation$`New Zealand`~world_unemployment$`New Zealand`), col = 'red', lwd = 4)
cor(world_unemployment$`New Zealand`, world_inflation$`New Zealand`)
#United States
plot(world_unemployment$`United States`, world_inflation$`United States`, 
     main = "Unemployment vs. Inflation (United States)", 
     xlab = "US Unemployment Rate", ylab = "US Inflation Rate", pch = 15)
abline(lm(world_inflation$`United States`~world_unemployment$`United States`), col = 'red', lwd = 4)
cor(world_unemployment$`United States`, world_inflation$`United States`)
#Nigeria
plot(world_unemployment$Nigeria, world_inflation$Nigeria,
     main = "Unemployment vs. Inflation (Nigeria)", 
     xlab = "Nigeria Unemployment Rate", ylab = "Nigeria Inflation Rate", pch = 15)
abline(lm(world_inflation$Nigeria~world_unemployment$Nigeria), col = 'red', lwd = 4)
cor(world_unemployment$Nigeria, world_inflation$Nigeria)
#South Africa
plot(world_unemployment$`South Africa`, world_inflation$`South Africa`, 
     main = "Unemployment vs. Inflation (South Africa)", 
     xlab = "South Africa Unemployment Rate", ylab = "South Africa Inflation Rate", pch = 15)
abline(lm(world_inflation$`South Africa`~world_unemployment$`South Africa`), col = 'red', lwd = 4)
cor(world_unemployment$`South Africa`, world_inflation$`South Africa`)
```

2)Graphical Comparisons(Unemployment)
```{r}
#United States
plot.new()
par(mar=c(5, 4, 4, 5) + 0.1)
plot(world_unemployment$`United States`, xlab = "", ylab = "", main = "US Unemployment Comparison",
     axes = FALSE, type = "b", pch = 16)
axis(2, at = seq(4, 10, by = 1), col="black",las=1)
mtext("US Unemployment",side=2,line=2.5)
box()
par(new = TRUE)
plot(GUS_unemp, pch = 15, type = 'b', xlab = '', ylab = '', main = '', axes = FALSE, col = 'red')
axis(4, at = seq(20, 65, by = 5), col = 'red', col.axis = 'red', las = 1)
mtext("Google Trend", side=4,col="red",line=2.5) 
axis(1, at = 1:8, labels = seq(2006, 2013, by = 1), las = 1)
mtext("Years", side=1, col="black",line=2.5) 
legend("topleft",legend=c("US Actual","Google Trend"),
       text.col=c("black","red"),pch=c(16,15),col=c("black","red"), cex = 0.9)
#Nigeria
plot.new()
par(mar=c(5, 4, 4, 5) + 0.1)
plot(world_unemployment$`Nigeria`, xlab = "", ylab = "", main = "Nigeria Unemployment Comparison",
     axes = FALSE, type = "b", pch = 16)
axis(2, at = seq(7.5, 7.6, by = 0.05), col="black",las=1)
mtext("Nigeria Unemployment",side=2,line=2.5)
box()
par(new = TRUE)
plot(GNig_unemp, pch = 15, type = 'b', xlab = '', ylab = '', main = '', axes = FALSE, col = 'red')
axis(4, at = seq(0, 40, by = 5), col = 'red', col.axis = 'red', las = 1)
mtext("Google Trend", side=4,col="red",line=2.5) 
axis(1, at = 1:8, labels = seq(2006, 2013, by = 1), las = 1)
mtext("Years", side=1, col="black",line=2.5) 
legend("left",legend=c("Nigeria Actual","Google Trend"),
       text.col=c("black","red"),pch=c(16,15),col=c("black","red"))
#South Africa
plot.new()
par(mar=c(5, 4, 4, 5) + 0.1)
plot(world_unemployment$`South Africa`, xlab = "", ylab = "", main = "South Africa Unemployment Comparison",
     axes = FALSE, type = "b", pch = 16)
axis(2, at = seq(22.5, 25.5, by = 0.5), col="black",las=1)
mtext("South Africa Unemployment",side=2,line=2.5)
box()
par(new = TRUE)
plot(GSA_unemp, pch = 15, type = 'b', xlab = '', ylab = '', main = '', axes = FALSE, col = 'red')
axis(4, at = seq(10, 40, by = 5), col = 'red', col.axis = 'red', las = 1)
mtext("Google Trend", side=4,col="red",line=2.5) 
axis(1, at = 1:8, labels = seq(2006, 2013, by = 1), las = 1)
mtext("Years", side=1, col="black",line=2.5) 
legend("bottomright",legend=c("South Africa Actual","Google Trend"),
       text.col=c("black","red"),pch=c(16,15),col=c("black","red"))
#Canada
plot.new()
par(mar=c(5, 4, 4, 5) + 0.1)
plot(world_unemployment$`Canada`, xlab = "", ylab = "", main = "Canada Unemployment Comparison",
     axes = FALSE, type = "b", pch = 16)
axis(2, at = seq(6, 8, by = 0.5), col="black",las=1)
mtext("South Africa Unemployment",side=2,line=2.5)
box()
par(new = TRUE)
plot(GCan_unemp, pch = 15, type = 'b', xlab = '', ylab = '', main = '', axes = FALSE, col = 'red')
axis(4, at = seq(10, 60, by = 5), col = 'red', col.axis = 'red', las = 1)
mtext("Google Trend", side=4,col="red",line=2.5) 
axis(1, at = 1:8, labels = seq(2006, 2013, by = 1), las = 1)
mtext("Years", side=1, col="black",line=2.5) 
legend("topleft",legend=c("Canada Actual","Google Trend"),
       text.col=c("black","red"),pch=c(16,15),col=c("black","red"), cex = 0.85)
#New Zealand
plot.new()
par(mar=c(5, 4, 4, 5) + 0.1)
plot(world_unemployment$`New Zealand`, xlab = "", ylab = "", main = "New Zealand Unemployment Comparison",
     axes = FALSE, type = "b", pch = 16)
axis(2, at = seq(4, 7, by = 0.5), col="black",las=1)
mtext("New Zealand Unemployment",side=2,line=2.5)
box()
par(new = TRUE)
plot(GCan_unemp, pch = 15, type = 'b', xlab = '', ylab = '', main = '', axes = FALSE, col = 'red')
axis(4, at = seq(15, 60, by = 5), col = 'red', col.axis = 'red', las = 1)
mtext("Google Trend", side=4,col="red",line=2.5) 
axis(1, at = 1:8, labels = seq(2006, 2013, by = 1), las = 1)
mtext("Years", side=1, col="black",line=2.5) 
legend("topleft",legend=c("New Zealand Actual","Google Trend"),
       text.col=c("black","red"),pch=c(16,15),col=c("black","red"),
       cex = 0.7)
```
2)Graphical Comparison(Inflation)
```{r}
#United States
plot.new()
par(mar=c(5, 4, 4, 5) + 0.1)
plot(world_inflation$`United States`, xlab = "", ylab = "", main = "US Inflation Comparison",
     axes = FALSE, type = "b", pch = 16)
axis(2, at = seq(0, 4, by = 1), col="black",las=1)
mtext("US Inflation",side=2,line=2.5)
box()
par(new = TRUE)
plot(GUS_inf, pch = 15, type = 'b', xlab = '', ylab = '', main = '', axes = FALSE, col = 'red')
axis(4, at = seq(35, 60, by = 5), col = 'red', col.axis = 'red', las = 1)
mtext("Google Trend", side=4,col="red",line=2.5) 
axis(1, at = 1:8, labels = seq(2006, 2013, by = 1), las = 1)
mtext("Years", side=1, col="black",line=2.5) 
legend("bottomleft",legend=c("US Actual","Google Trend"),
       text.col=c("black","red"),pch=c(16,15),col=c("black","red"), cex = 0.9)
#Nigeria
plot.new()
par(mar=c(5, 4, 4, 5) + 0.1)
plot(world_inflation$`Nigeria`, xlab = "", ylab = "", main = "Nigeria Inflation Comparison",
     axes = FALSE, type = "b", pch = 16)
axis(2, at = seq(5, 15, by = 2), col="black",las=1)
mtext("Nigeria Inflation",side=2,line=2.5)
box()
par(new = TRUE)
plot(GNig_inf, pch = 15, type = 'b', xlab = '', ylab = '', main = '', axes = FALSE, col = 'red')
axis(4, at = seq(5, 30, by = 5), col = 'red', col.axis = 'red', las = 1)
mtext("Google Trend", side=4,col="red",line=2.5) 
axis(1, at = 1:8, labels = seq(2006, 2013, by = 1), las = 1)
mtext("Years", side=1, col="black",line=2.5) 
legend("topleft",legend=c("Nigeria Actual","Google Trend"),
       text.col=c("black","red"),pch=c(16,15),col=c("black","red"), cex = 0.9)
#South Africa
plot.new()
par(mar=c(5, 4, 4, 5) + 0.1)
plot(world_inflation$`South Africa`, xlab = "", ylab = "", main = "South Africa Inflation Comparison",
     axes = FALSE, type = "b", pch = 16)
axis(2, at = seq(4, 12, by = 2), col="black",las=1)
mtext("South Africa Inflation",side=2,line=2.5)
box()
par(new = TRUE)
plot(GSA_inf, pch = 15, type = 'b', xlab = '', ylab = '', main = '', axes = FALSE, col = 'red')
axis(4, at = seq(10, 35, by = 5), col = 'red', col.axis = 'red', las = 1)
mtext("Google Trend", side=4,col="red",line=2.5) 
axis(1, at = 1:8, labels = seq(2006, 2013, by = 1), las = 1)
mtext("Years", side=1, col="black",line=2.5) 
legend("topright",legend=c("US Actual","Google Trend"),
       text.col=c("black","red"),pch=c(16,15),col=c("black","red"), cex = 0.8)
#Canada
plot.new()
par(mar=c(5, 4, 4, 5) + 0.1)
plot(world_inflation$`Canada`, xlab = "", ylab = "", main = "Canada Inflation Comparison",
     axes = FALSE, type = "b", pch = 16)
axis(2, at = seq(0.5, 3, by = 0.5), col="black",las=1)
mtext("US Canada",side=2,line=2.5)
box()
par(new = TRUE)
plot(GCan_inf, pch = 15, type = 'b', xlab = '', ylab = '', main = '', axes = FALSE, col = 'red')
axis(4, at = seq(32, 44, by = 4), col = 'red', col.axis = 'red', las = 1)
mtext("Google Trend", side=4,col="red",line=2.5) 
axis(1, at = 1:8, labels = seq(2006, 2013, by = 1), las = 1)
mtext("Years", side=1, col="black",line=2.5) 
legend("bottomleft",legend=c("Canada Actual","Google Trend"),
       text.col=c("black","red"),pch=c(16,15),col=c("black","red"),
       cex = 0.7)
#New Zealand
plot.new()
par(mar=c(5, 4, 4, 5) + 0.1)
plot(world_inflation$`New Zealand`, xlab = "", ylab = "", main = "New Zealand Inflation Comparison",
     axes = FALSE, type = "b", pch = 16)
axis(2, at = seq(0, 4.5, by = 0.5), col="black",las=1)
mtext("New Zealand Inflation",side=2,line=2.5)
box()
par(new = TRUE)
plot(GNZ_inf, pch = 15, type = 'b', xlab = '', ylab = '', main = '', axes = FALSE, col = 'red')
axis(4, at = seq(2, 16, by = 2), col = 'red', col.axis = 'red', las = 1)
mtext("Google Trend", side=4,col="red",line=2.5) 
axis(1, at = 1:8, labels = seq(2006, 2013, by = 1), las = 1)
mtext("Years", side=1, col="black",line=2.5) 
legend("topleft",legend=c("US Actual","Google Trend"),
       text.col=c("black","red"),pch=c(16,15),col=c("black","red"),
       cex = 0.65)
```
3) See the relationship between Unemployment and Inflation between different countries using Google data
```{r}
#United States
par(mar = c(5, 4, 4, 2) + 0.1)
plot(GUS_unemp, GUS_inf, 
     main = "Google Unemployment vs. Inflation (United States)", 
     xlab = "US Unemployment Search Freq", ylab = "US Inflation Search Freq", pch = 16)
abline(lm(GUS_inf~GUS_unemp), col = 'red', lwd = 4)
cor(GUS_inf, GUS_unemp)
#Nigeria
par(mar = c(5, 4, 4, 2) + 0.1)
plot(GNig_unemp, GNig_inf, 
     main = "Google Unemployment vs. Inflation (Nigeria)", 
     xlab = "Nigeria Unemployment Search Freq", ylab = "Nigeria Inflation Search Freq", pch = 16)
abline(lm(GNig_inf~GNig_unemp), col = 'red', lwd = 4)
cor(GNig_inf, GNig_unemp)
#South Africa
par(mar = c(5, 4, 4, 2) + 0.1)
plot(GSA_unemp, GSA_inf, 
     main = "Google Unemployment vs. Inflation (South Africa)", 
     xlab = "South Africa Unemployment Search Freq", ylab = "South Africa Inflation Search Freq", pch = 16)
abline(lm(GSA_inf~GSA_unemp), col = 'red', lwd = 4)
cor(GSA_inf, GSA_unemp)
#Canada
par(mar = c(5, 4, 4, 2) + 0.1)
plot(GCan_unemp, GCan_inf, 
     main = "Google Unemployment vs. Inflation (Canada)", 
     xlab = "Canada Unemployment Search Freq", ylab = "Canada Inflation Search Freq", pch = 16)
abline(lm(GCan_inf~GCan_unemp), col = 'red', lwd = 4)
cor(GCan_inf, GCan_unemp)
#New Zealand
par(mar = c(5, 4, 4, 2) + 0.1)
plot(GNZ_unemp, GNZ_inf, 
     main = "Google Unemployment vs. Inflation (New Zealand)", 
     xlab = "New Zealand Unemployment Search Freq", ylab = "New Zealand Inflation Search Freq", pch = 16)
abline(lm(GNZ_inf~GNZ_unemp), col = 'red', lwd = 4)
cor(GNZ_inf, GNZ_unemp)

```
4)Graphical Comparison of Phillips Curve (World Data vs. Google)
```{r}
#United States
plot.new()
par(mar = c(5, 4, 5.5, 5) + 0.1)
plot(world_unemployment$`United States`, world_inflation$`United States`, 
     main = "", 
     xlab = "", ylab = "", pch = 15, axes = FALSE)
abline(lm(world_inflation$`United States`~world_unemployment$`United States`), col = 'black', lwd = 4)
axis(2, at = seq(0, 4, by = 1), col="black",las=1)
mtext("US Inflation", side=2, col="black",line=2) 
axis(1, at = seq(5, 9, by = 1), col="black",las=1)
mtext("US Unemployment", side=1, col="black",line=2) 
box()
par(new = TRUE)
plot(GUS_unemp, GUS_inf,
     xlab = "", ylab = "", pch = 16, axes = FALSE, col = "red", main = '')
axis(4, at = seq(35, 55, by = 5), col="red",las=1, col.axis = 'red')
mtext("Google Inflation", side=4, col="red",line=2) 
axis(3, at = seq(20, 60, by = 10), col="red",las=1, col.axis = 'red')
mtext("Google Unemployment", side=3, col="red",line=2) 
abline(lm(GUS_inf~GUS_unemp), col = 'red', lwd = 4)
legend("bottomleft",legend=c("US","Google"),
       text.col=c("black","red"),pch=c(16,15),col=c("black","red"))
title("US Phillips Curve (Actual vs. Google)", line = 3.5)
#Nigeria
plot.new()
par(mar = c(5, 4, 5.5, 5) + 0.1)
plot(world_unemployment$`Nigeria`, world_inflation$`Nigeria`, 
     main = "", 
     xlab = "", ylab = "", pch = 15, axes = FALSE)
abline(lm(world_inflation$`Nigeria`~world_unemployment$`Nigeria`), col = 'black', lwd = 4)
axis(2, at = seq(6, 14, by = 2), col="black",las=1)
mtext("Nigeria Inflation", side=2, col="black",line=2) 
axis(1, at = seq(7.5, 7.6, by = 0.02), col="black",las=1)
mtext("Nigeria Unemployment", side=1, col="black",line=2) 
box()
par(new = TRUE)
plot(GNig_unemp, GNig_inf,
     xlab = "", ylab = "", pch = 16, axes = FALSE, col = "red", main = '')
axis(4, at = seq(5, 30, by = 5), col="red",las=1, col.axis = 'red')
mtext("Google Inflation", side=4, col="red",line=2) 
axis(3, at = seq(5, 40, by = 5), col="red",las=1, col.axis = 'red')
mtext("Google Unemployment", side=3, col="red",line=2) 
abline(lm(GNig_inf~GNig_unemp), col = 'red', lwd = 4)
legend("bottom",legend=c("Nigeria","Google"),
       text.col=c("black","red"),pch=c(16,15),col=c("black","red"))
title("Nigeria Phillips Curve (Actual vs. Google)", line = 3.5)
#South Africa
plot.new()
par(mar = c(5, 4, 5.5, 5) + 0.1)
plot(world_unemployment$`South Africa`, world_inflation$`South Africa`, 
     main = "", 
     xlab = "", ylab = "", pch = 15, axes = FALSE)
abline(lm(world_inflation$`South Africa`~world_unemployment$`South Africa`), col = 'black', lwd = 4)
axis(2, at = seq(4, 12, by = 2), col="black",las=1)
mtext("South Africa Inflation", side=2, col="black",line=2) 
axis(1, at = seq(22, 25, by = 0.5), col="black",las=1)
mtext("South Africa Unemployment", side=1, col="black",line=2) 
box()
par(new = TRUE)
plot(GSA_unemp, GSA_inf,
     xlab = "", ylab = "", pch = 16, axes = FALSE, col = "red", main = '')
axis(4, at = seq(5, 35, by = 5), col="red",las=1, col.axis = 'red')
mtext("Google Inflation", side=4, col="red",line=2) 
axis(3, at = seq(10, 35, by = 5), col="red",las=1, col.axis = 'red')
mtext("Google Unemployment", side=3, col="red",line=2) 
abline(lm(GSA_inf~GSA_unemp), col = 'red', lwd = 4)
legend("topleft",legend=c("South Africa","Google"),
       text.col=c("black","red"),pch=c(16,15),col=c("black","red"), cex = 0.5)
title("South Africa Phillips Curve (Actual vs. Google)", line = 3.5)
#Canada
plot.new()
par(mar = c(5, 4, 5.5, 5) + 0.1)
plot(world_unemployment$`Canada`, world_inflation$`Canada`, 
     main = "", 
     xlab = "", ylab = "", pch = 15, axes = FALSE)
abline(lm(world_inflation$`Canada`~world_unemployment$`Canada`), col = 'black', lwd = 4)
axis(2, at = seq(0.5, 3, by = 0.5), col="black",las=1)
mtext("Canada Inflation", side=2, col="black",line=2) 
axis(1, at = seq(6, 8, by = 1), col="black",las=1)
mtext("Canada Unemployment", side=1, col="black",line=2) 
box()
par(new = TRUE)
plot(GCan_unemp, GCan_inf,
     xlab = "", ylab = "", pch = 16, axes = FALSE, col = "red", main = '')
axis(4, at = seq(32, 44, by = 2), col="red",las=1, col.axis = 'red')
mtext("Google Inflation", side=4, col="red",line=2) 
axis(3, at = seq(20, 50, by = 10), col="red",las=1, col.axis = 'red')
mtext("Google Unemployment", side=3, col="red",line=2) 
abline(lm(GCan_inf~GCan_unemp), col = 'red', lwd = 4)
legend("topright",legend=c("US","Google"),
       text.col=c("black","red"),pch=c(16,15),col=c("black","red"))
title("Canada Phillips Curve (Actual vs. Google)", line = 3.5)
#New Zealand
plot.new()
par(mar = c(5, 4, 5.5, 5) + 0.1)
plot(world_unemployment$`New Zealand`, world_inflation$`New Zealand`, 
     main = "", 
     xlab = "", ylab = "", pch = 15, axes = FALSE)
abline(lm(world_inflation$`New Zealand`~world_unemployment$`New Zealand`), col = 'black', lwd = 4)
axis(2, at = seq(0, 4, by = 1), col="black",las=1)
mtext("New Zealand Inflation", side=2, col="black",line=2) 
axis(1, at = seq(4, 7, by = 0.5), col="black",las=1)
mtext("New Zealand Unemployment", side=1, col="black",line=2) 
box()
par(new = TRUE)
plot(GNZ_unemp, GNZ_inf,
     xlab = "", ylab = "", pch = 16, axes = FALSE, col = "red", main = '')
axis(4, at = seq(5, 15, by = 5), col="red",las=1, col.axis = 'red')
mtext("Google Inflation", side=4, col="red",line=2) 
axis(3, at = seq(0, 50, by = 5), col="red",las=1, col.axis = 'red')
mtext("Google Unemployment", side=3, col="red",line=2) 
abline(lm(GNZ_inf~GNZ_unemp), col = 'red', lwd = 4)
legend("bottom",legend=c("New Zealand","Google"),
       text.col=c("black","red"),pch=c(16,15),col=c("black","red"))
title("New Zealand Phillips Curve (Actual vs. Google)", line = 3.5)
```

